Relationships in the extremes and their influence on competition and coexistence

### 2022-03-22 paper/Paper.Rnw
adding to discussion

%We note that our expansion, like the decomposition of \cite{Ellner_2019} is generalizable to multi-species and multi-driver models. Because asymmetric tail associations exist in many ecological variables \citep{Ghosh_2020_AER}, the more specified approach of considering unique drivers of coexistence rather than E and C and the ability to consider more than two drivers, could produce interesting results?? 
%More species and more drivers= more things that can be related
The extended decomposition of storage effects and quantification of ATA contribution to coexistence can and 
should also be applied to multi-species models. 
The inclusion of multiple species introduces a multitude of relationships between species'
environmentally dependent parameters that could possibly be asymmetrically associated. 
The greater the number of species the greater the possibilities of ATAs being more important 
to their coexistence.

The probability of ATAs being important for the coexistence of species increases as more variables are included in the system, 
either through the addition of more species or more drivers (beyond just E and C), or both. 
When multiple species are included in the system, the interaction between different species' E's and C's introduces more relationships 
to consider that may or may not be asymmetrically related and could increase the relative importance of ATA contribution to the species' coexistence. 
Likewise, coexistence between species can also depend on more than two drivers \citep{Ellner_2019}. 
%notation in ellner one could also use partial sharp 
%reread ellner paper 
%make three different biv dis that are standard normal copula and then pair with a shuffles third
%use to get rbar and subtract from rbar of XY#Z,

>>>>

%Because asymmetric tail associations exist in many ecological variables \citep{Ghosh_2020_AER}, the more specified approach of considering unique drivers of coexistence rather than E and C and the ability to consider more than two drivers, could produce interesting results??

%The inclusion of multiple species introduces a multitude of relationships between species'
%environmentally dependent parameters that could possibly be asymmetrically associated. 
%The greater the number of species the greater the possibilities of ATAs being more important 
%to their coexistence.

The chances of ATAs being important for the coexistence of species increases as more variables are included in the system, 
either through the addition of more species or more drivers (beyond just E and C), or both. 
When multiple species are included in the system, the interaction between different species' E's and C's introduces more relationships 
to consider that may or may not be asymmetrically related and could increase the relative importance of ATA contribution to the species' coexistence. 
Likewise, coexistence between species can also depend on more than two drivers \citep{Ellner_2019}. 
The storage effect decomposition presented here is generalizable to coexistence decompositions of multiple variables.
Following the set up and notation of \cite{Ellner_2019}'s \emph{covariance decomposition}, 
ATA contributions and correlation \emph{per se} can be decomposed from the \emph{associations} between two variables
among many from the appropriate term with parenthesized superscripts with the # symbol denoting and separating 
variables that are varying independently from the variables that are covarying whose relationship we are interested in decomposing. 
For example, the term $\Delta^{(XY#Z)}$ could be decomposed into $\Delta^{[XY#Z]} + \Delta^{[X \nat Y#Z]}$. 
As more terms and species are introduced into a system, more relationships between variables must be evaluated,
more of those relationships may be asymmetrically tail associated, and ATAs may contribute more to the maintenance of 
biodiversity in that system. 
%make three different biv dis that are standard normal copula and then pair with a shuffles third
%use to get rbar and subtract from rbar of XY#Z,
